Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-09-26 paper.qmd
Figure 13 added rectangles for selected clusters

trimesh_removed_gau_umap <- ggplot() + 
  geom_segment(data = tr_from_to_df_gau1, 
               aes(
                 x = x_from, 
                 y = y_from, 
                 xend = x_to, 
                 yend = y_to),
               colour = "#000000",
               linewidth = 1) +
  geom_point(
    data = umap_gau_scaled,
    aes(
      x = UMAP1,
      y = UMAP2
    ),
    alpha = 0.05,
    #size = 0.1,
    color = "#999999"
  )  +
  interior_annotation("b1", 
                      position = c(0.06, 0.95),
                      cex = 2) +
  theme(
    aspect.ratio = 1
  )

@@

trimesh_removed_gau_pacmap <- ggplot() + 
  geom_segment(data = tr_from_to_df_gau1, 
               aes(
                 x = x_from, 
                 y = y_from, 
                 xend = x_to, 
                 yend = y_to),
               colour = "#000000",
               linewidth = 1) +
  geom_point(
    data = pacmap_gau_scaled,
    aes(
      x = PaCMAP1,
      y = PaCMAP2
    ),
    alpha = 0.3,
    #size = 0.1,
    color = "#999999"
  )  +
  interior_annotation("c1", 
                      position = c(0.08, 0.95),
                      cex = 2) +
  theme(
    aspect.ratio = 1
  )

>>>>

trimesh_removed_gau_umap <- ggplot() + 
  geom_segment(data = tr_from_to_df_gau1, 
               aes(
                 x = x_from, 
                 y = y_from, 
                 xend = x_to, 
                 yend = y_to),
               colour = "#000000",
               linewidth = 1) +
  geom_point(
    data = umap_gau_scaled,
    aes(
      x = UMAP1,
      y = UMAP2
    ),
    alpha = 0.05,
    #size = 0.1,
    color = "#999999"
  ) + 
  geom_rect(
    aes(xmin = 0.45, 
        xmax = 0.57, 
        ymin = 0, 
        ymax = 0.1),
    fill = "transparent", 
    color = "red", 
    linewidth = 0.5)  +
  interior_annotation("b1", 
                      position = c(0.06, 0.95),
                      cex = 2) +
  theme(
    aspect.ratio = 1
  )

@@

trimesh_removed_gau_pacmap <- ggplot() + 
  geom_segment(data = tr_from_to_df_gau1, 
               aes(
                 x = x_from, 
                 y = y_from, 
                 xend = x_to, 
                 yend = y_to),
               colour = "#000000",
               linewidth = 1) +
  geom_point(
    data = pacmap_gau_scaled,
    aes(
      x = PaCMAP1,
      y = PaCMAP2
    ),
    alpha = 0.3,
    #size = 0.1,
    color = "#999999"
  ) +
  geom_rect(
    aes(xmin = -0.04, 
        xmax = 0.22, 
        ymin = 0.08, 
        ymax = 0.34),
    fill = "transparent", 
    color = "red", 
    linewidth = 0.5) +
  interior_annotation("c1", 
                      position = c(0.08, 0.95),
                      cex = 2) +
  theme(
    aspect.ratio = 1
  )
